This work was supported by DOE grant number A, and NSF grant number B.

We thank Gabriel Orebi Gann of University of California, Berkeley for discussion on expected backgrounds at 
SNO+ experiment. We thank Jenni Kotilla of Yale for discussions on electron angular correlations in 0\nbb-decay 
and for providing data with phase factors for generating 0\nbb- and 2\nbb-decay events.
We are greateful to Christoph Aberle, formely at UCLA, for initial development of Geant-4 
detector model used at this paper and early contribution to the development of Cherekov/scintillation
light separation technique. We thank Matthew Wetstein of the Iowa State University for help with vertex reconsruction
algoroithms and productive discussion on Cherenkov/scintillation light separation (\textbf{unless Matt wants to be
an author}). We thank Eric Spieglan of the University of Chicago for productive discussions on spherical harmonics
analysis. We also thank Evan Angelico of the University of Chicago for estimating effects of photo-detector position and
time resolution on the vertex reconstruction and verifying effects of chromatic dispersions. We thank Carla Pilcher of 
the University of Chicago for discussions on gammas interactions in liquid scintillators.
We thank Davide Franco of CNRS and Paolo Crivelli of ETH, Zurich for sharing their experience with ortho-positronium 
simulation in Geant-4. We thank Jan Flusser of Institute of Information Theory and Automation, Czech Academy of Sciences for
helpfull discussions on image processing using moment invariants. Last but not least we thank Mingfang Yeh of 
Brookhaven National Laboratory for discussions of timing properties of various liquid scintillators.
